Population structure and phenotypic variation of \emph{Sclerotinia sclerotiorum} from dry bean in the United States

### 2017-09-29 doc/manuscript/manuscript.tex
fix spelling of Sajeewa's name :no_mouth:
update pdf manuscript

\author[1]{Bimal Sajeewa Amadarasa}

@@

\affil[1]{Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln
68583}

@@

\emph{Sclerotinia sclerotiorum} (Lib.) de Bary is an ascomycete plant
pathogen with a worldwide distribution. This is a necrotrophic pathogen
that is primarily homothallic (self-fertilization) and has the ability
to survive for more than five years in soil using melanized survival
structures called sclerotia (Bolton et al., 2006; Sexton et al., 2006).
It causes disease on more than 400 plant species belonging to 75
families (Boland \& Hall, 1994) including crops of major economic
importance such as sunflower (\emph{Helianthus spp.}), soybean
(\emph{Glycine max} L.), canola (\emph{Brassica napa} L., \emph{Brassica
campestris} L.), and dry bean (\emph{Phaseolus vulgaris} L.) (Bolton et
al., 2006). On dry bean, \emph{S. sclerotiorum} is the causal agent of
white mold, a devastating disease that can be a yield-limiting in
temperate climates (Steadman, 1983).

Currently, there are no known resistant cultivars of dry bean
commercially available (Otto-Hanson et al., 2011). Organized breeding
efforts have used a common-garden approach with white mold screening
nurseries in dry bean production areas across the United States with
additional sites in Mexico, France, and Australia (Steadman et al.,
2003, 2004, 2005, 2006; Otto-Hanson \& Steadman, 2007, 2008; McCoy \&
Steadman, 2009). These white mold screening nurseries use no chemical or
cultural treatments against \emph{S. sclerotiorum} and employ
standardized protocols for screening new cultivars for resistance to
white mold. It has previously been shown that aggressiveness (the
severity of disease symptoms on the host) is significantly different
across white mold screening nursery sites in separate geographic regions
(Otto-Hanson et al., 2011). The genetic structure and mode of
reproduction in these populations, however, is currently unknown.

@@

In this study, we analyze and characterize the genetic and phenotypic
diversity of 366 \emph{S. sclerotiorum} isolates collected over 10 years
between 2003 and 2012 from dry bean cultivars among different geographic
locations in the United States, France, Mexico, and Australia. We wanted
to know if the \emph{S. sclerotiorum} populations from white mold
screening nurseries were representative of the fields within the same
region. As these nurseries were not treated with any chemical or
cultural control of white mold, we hypothesized that these nurseries
would represent the natural population of \emph{S. sclerotiorum}.
Furthermore, we wanted to investigate the potential effect of cultivar
on genetic diversity by assessing three dry bean cultivars with
different levels of resistance, Beryl (great northern bean,
susceptible), Bunsi (navy bean, low susceptibility), and G122 (cranberry
bean, partial resistance) (Otto-Hanson et al., 2011). We additionally
wanted to determine categorical or phenotypic variables that best
predicted genetic structure and if there was correlation between
multilocus haplotype and mycelial compatibility group. Knowing what
variables predict genetic structure can help direct breeding efforts. By
investigating these aims, we hope to effectively describe the population
structure of \emph{S. sclerotiorum} in the USA and make available our
database of isolates for use in future dry bean breeding efforts.

@@

Several of the isolates used for this study were collected as reported
in previous studies using the same methods (Otto-Hanson et al., 2011).
Broadly, isolates were collected from two sources: white mold screening
nurseries (wmn) or producer fields. White mold screening nurseries were
5m x 10m in size and maintained without application of fungicides to
observe natural incidence of white mold. The nursery plots were
incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of
0:3:2 during the growing season (Steadman et al., 2003).

@@

Sclerotia of \emph{S. sclerotiorum} were collected over several years
from grower fields and/or wmn in 11 states of the United States of
America, Mexico, France, and Australia (Table \ref{tab:isolate-table}).
After collection, sclerotia were stored in Petri plates lined with
filter paper, then stored at \(20~^{\circ}\)F or -\(4~^{\circ}\)C.
Sclerotia were surface-sterilized with 50\% Clorox bleach (at least 6\%
NaOCL, The Clorox Company, Oakland, CA) solution for 3 min, and double
rinsed with ddH\(_2\)O 3 min. The sterilized sclerotia were then placed
on water agar plates (16g of Bacto agar per liter of ddH\(_2\)O, BD
Diagnostic Systems, Sparks, MD), with four to five sclerotia of each
isolate separated on each plate and stored on the counter top at room
temperature for 5 to 6 days. An 8-mm plug from a 5- or 6-day-old culture
was transferred from the advancing margin of the mycelia onto a plate of
Difco potato dextrose agar (PDA at 39 g/liter of ddH\(_2\)O)
(Otto-Hanson et al., 2011). In combination with the 156 isolates
described previously, we collected 210 isolates for a total of 366
isolates (Otto-Hanson et al., 2011).

@@

Aggressiveness of each isolate was assessed using a straw test as
described in Otto-Hanson et al. (2011) that rated necrotic lesion size
(Petzoldt \& Dickson, 1996; Teran et al., 2006). Briefly, the straw test
uses 21-day-old G122 plants as the host in a greenhouse setting. Clear
drinking straws cut to 2.5 cm and sealed were used to place two mycelial
plugs of inoculum on the host plant after removing all plant growth
\textgreater{}2.5 cm above the fourth node. Measurements of the necrotic
lesion were taken 8 days later using the Modified Petzoldt and Dickson
scale of 1--9, where 1 is no disease and 9 is plant death (Petzoldt \&
Dickson, 1996; Teran et al., 2006).

@@

Prior to DNA extraction, isolates were grown on PDA and plugs were
subsequently transferred to Potato Dextrose Broth (PDB) where they were
grown until there was significant mycelial growth, but before the
mycelial mat became solidified (4--5 days). Mycelia for each plate was
collected in a buchner funnel, agar plugs removed, lyophilized and
pulverized manually in Whirl-pak® HDPE sampling bags (Sigma-Aldrich,
St.~Louis, MO). Lyophilized mycelia was then stored in microcentrifuge
tubes at -\(20~^{\circ}\)C until needed for DNA extraction. DNA from
25mg of pulverized mycelia was purified using a phenol-chloroform
extraction method followed by alcohol precipitation and evaporation,
suspending the DNA in 200\(\mu\)l TE (Sambrook et al., 1989). Suspended
DNA was stored at \(4~^{\circ}\)C until genotyping.

@@

After clone-correction on the hierarchy of Region/Source/Host/Year, we
were left with 318 isolates representing 165 MLHs (Table
\ref{tab:iatab}). The results show that most populations exhibited
relatively high amounts of genotypic diversity, with the exception of MI
and NE, which exhibited lower-than average \(E_5\) values. Mexico had
the lowest average value of gene diversity, \emph{h} and the lowest
\emph{eMLH}, suggesting low overall genetic diversity. Nearly all
populations showed evidence for linkage (Table \ref{tab:iatab}), which
serves as evidence for clonal reproduction or other forms of non-random
mating. The only exceptions are CA and Australia. Both of these
populations showed only moderate significance (P \textless{} 0.05) with
\(\bar{r}_d\) values of 0.03 and 0.12, respectively.

\begin{longtable}[]{@{}lrrrrr@{}}

@@

\begin{minipage}[b]{0.09\columnwidth}\raggedright\strut

@@

\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedleft\strut

@@

@@

\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut

@@

\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedleft\strut

@@

@@

\begin{longtable}[]{@{}lrrrrrrrl@{}}

@@

@@

\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedleft\strut

@@

@@

@@

\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedleft\strut

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/mcg-subgraph-with-context.pdf}
\caption{Associations between Mycelial Compatibility Groups and
Multilocus Haplotypes. \textbf{A)} Barplot of Mycelial Compatibility
Group (MCG) abundance in descending order. Singletons (46) were
truncated, leaving 41 MCGs. White bars represent sample counts and grey
bars represent counts of unique multilocus haplotypes (MLH). The
transparency of the bars represent the evenness of the distribution of
the MLHs within a given MCG. A dashed box surrounds the eight most
common MCGs representing \textgreater{}~51\% of the data. \textbf{B)}
Full graph-representation of the relationship between MCGs (open
circles) and MLHs (filled circles). Details in Fig. \ref{fullgraph}.
\textbf{C)} A subset of \textbf{B} representing the 8 most common MCGs
and their associated MLHs (dashed box in \textbf{A}). Filled nodes
(circles) represent MLHs and open nodes represent MCGs. Node area scaled
to the number of samples represented (range: 1--73). Numbers inside
nodes are the MLH/MCG label (if n \textgreater{} 1). Edges (arrows)
point from MLH to MCG where the weight (thickness) of the edge
represents the number of shared isolates (range: 1--19). Edges extending
from MLHs displayed to other MCGs are not shown.}\label{biggraph}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Figure7Z.pdf}
\caption{Biplot showing five most influential explanatory variables
(arrows) overlayed on the first two eigenvectors of distance based
redundancy analysis of \emph{Sclerotinia sclerotiorum} isolates. The
length of the arrows are directly proportional to the strength of the
correlation between explanatory and molecular variables. Open circles
represent the 318 clone-corrected haplotypes in ordination
space.}\label{rda-biplot}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{../../results/figures/publication/aggressiveness.pdf}
\caption{Strip Plot of aggressiveness by population arranged in
descending order of mean aggressiveness for all populations with N
\textgreater{} 5. White bars represent mean value. Circles represent
individual isolates where filled circles are isolates from white mold
screening nurseries (wmn) and open circles are isolates from producer
fields.}\label{aggressiveness-boxplot}
\end{figure}

The forward-backward selection process of the dbRDA models on
clone-corrected data revealed Year, Region, Host, and MCG to be the
optimal variables for the reduced model, accounting for 45\% of the
total variation. ANOVA showed that the reduced model was significant
with an adjusted R\textsuperscript{2} of 0.0675 (\emph{P} = 0.001).
Assessment of the marginal effects showed that all varaibles
significantly explained genetic variation (\emph{P} = 0.001, \emph{P} =
0.007 for Region). We found that there was multicollinearity when MCG
was combined with any other variable, so repeated the analysis, dropping
MCG from the list of potential predictors. From these results, Year,
Region, Host, and Aggressiveness were found to be optimal, accounting
for 17.6\% of the total variation. ANOVA revealed significant effects
with an adjusted R\textsuperscript{2} of 0.0325 (\emph{P} = 0.001).
While the marginal effect assessment revealed that Year, Region, and
Host significantly explained variation at \emph{P} = 0.001, and
Aggressiveness significantly explained variation at \emph{P} = 0.039.
Much of the variation appeared to be driven by isolates from Mexico and
2005 (Fig. \ref{rda-biplot}). Variance partitioning of the independent
variables without MCG indicated aggressiveness to be the least
influential factor with 0.1\% contributing to explaining the variation
of molecular data, whereas the combination of variables accounted for
3.3\%.

@@

Agressiveness of the isolates ranged from 1.4 to 7.9 with a mean of 5.02
and median of 4.85. The group mean averages were 4.88, 5.13, and 5.19
for Region, MCG, and MLH, respectively. Our assessment of aggressiveness
in association with Region showed a significant effect (\emph{P}
\textless{} 1.00e\textsuperscript{-4}), with means that ranged from 5.8
(MN) to 4.0 (CA) (Fig. \ref{aggressiveness-boxplot}, Table
\ref{tab:region-aggressiveness}). MCGs also showed a significant effect
(\emph{P} \textless{} 1.00e\textsuperscript{-4}), with means that ranged
from 6.0 (`MCG 44') to 4.6 (`MCG 49'; Table
\ref{tab:MCG-aggressiveness}). We additionally found a significant
effect for MLHs (\emph{P} = 7.44e\textsuperscript{-4}) for MLHs, with
means that ranged from 6.0 (`MLH 78') to 4.3 (`MLH 140') (Table
\ref{tab:MLG-aggressiveness}).

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/mlg-11.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) genotyped over 11 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/DAPC.pdf}
\caption{Discriminant Analysis of Principal Components on regions
showing that Mexico is differentiated from other populations.
\textbf{A)} Scatter plot of first two components from DAPC. Points
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. \textbf{B)} Mean population assignment probability from the DAPC
for all populations with N \textgreater{} 10 (facets). Populations
represented along the horizontal axis and probability of assignment on
the vertical. Numbers next to source populations indicate population
size. All values sum to one.}\label{DAPC}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/dapc_region_year_micanewa.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
on Regions and Years showing non-differentiated temporal variation NE
and MI and temporal variation in WA and CA. Points (text labels)
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. A more detailed view is shown in Fig.
\ref{DAPC-RY-FULL}.}\label{DAPC-RY}
\end{figure}

@@

Despite the evidence that Mexico and CA contributed to much of the
population differentiation, Regions like WA still had a large amount of
internal variation. The two distinct clusters for the WA Region showed
that the 2008 population appeared differentiated and, under further
investigation, we found that all the haplotypes from this year were
shared between CA and France (Fig. \ref{community-graph}, \ref{DAPC-RY},
\ref{DAPC-RY-FULL}). All of the isolates from WA in 2003--2005, and 2008
came from the same wmn; within the wmn, those in 2003--2005 came a
Northeastern field location cropped with dry bean since 2002, and those
in 2008 from a Southeastern field that was previously cropped with
brassica, sundgrass, peas, beans, and potatoes (Miklas, Phil Pers.
comm.). Both of these fields were inoculated with sclerotia in 2002, the
Northeastern field with sclerotia provided by a commercial bean producer
and the Southeastern field with sclerotia from peas (although this was
thought to be unsuccessful). Despite this information, it is still
unclear what has contributed to the differentiation of the 2008
population from WA. While the evidence my suggest host as being a
factor, previous studies have shown no significant differentiation
across host species (Aldrich-Wolfe et al., 2015).

@@

One long-held assumption was that MCGs (as determined via barrage
reaction) represent vegetative compatibility groups (VCGs) (Kohn et al.,
1990; Schafer \& Kohn, 2006; Lehner et al., 2015), which are known to
have a genetic component (Saupe, 2000; Hall et al., 2010; Strom \&
Bushley, 2016). While our protocol for assessing MCGs utilized a
different substrate for the MCG reactions, the patterns we observe are
not dissimilar from what have previously been reported in the
literature. It has been demonstrated in several Ascomycetes---including
\emph{Neurospora crassa} (Micali \& Smith, 2003), \emph{Sclerotinia
homoecarpa} (Jo et al., 2008), \emph{Verticillium dahliae} (Papaioannou
\& Typas, 2014), and \emph{S. sclerotiorum} (Ford et al., 1995)---that
barrage reactions are independent from stable anastomosis. Thus, the
inconsistencies in this study and other studies indicate that
researchers studying \emph{S. sclerotiorum} should not rely on MCG data
derived from barrage reactions as an indicator for genetic diversity.

@@

This study represents the largest genetic analysis of \emph{S.
sclerotiorum} from the USA to date, giving us a unique insight to
continent-wide population structure and relationships between phenotypic
and genotypic variables. Populations in wmn appear to show no
significant differentiation when compared to their production field
counterparts, suggesting that the wmn populations of \emph{S.
sclerotiorum} may be considered representative of the surrounding
regions. While we found no direct relationship between haplotype and
severity, it is evident that there is a gradient of severity by region,
further supporting the need for screening in multiple locations. Based
on our analysis of the relationships between MCG and MLH, we found no
clear evidence that the two are directly related, suggesting that MCG do
not necessarily represent vegetative compatibility groups and thus
should not be used as a proxy for identifying clones.

>>>>

\author[1]{Bimal Sajeewa Amaradasa}

@@

\affil[1]{Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln,
NE 68583}

@@

\emph{Sclerotinia sclerotiorum} (Lib.) de Bary is an ascomycete plant
pathogen with a worldwide distribution. This is a necrotrophic pathogen
that is primarily homothallic (self-fertilization) and has the ability
to survive for more than five years in soil using melanized survival
structures called sclerotia (Bolton et al., 2006; Sexton et al., 2006).
It causes disease on more than 400 plant species belonging to 75
families (Boland \& Hall, 1994) including crops of major economic
importance such as sunflower (\emph{Helianthus spp.}), soybean
(\emph{Glycine max} L.), canola (\emph{Brassica napa} L., \emph{Brassica
campestris} L.), and dry bean (\emph{Phaseolus vulgaris} L.) (Bolton et
al., 2006). On dry bean, \emph{S. sclerotiorum} is the causal agent of
white mold, a devastating disease that can be yield-limiting in
temperate climates (Steadman, 1983).

Currently, there are no commercially available resistant cultivars of
dry bean (Otto-Hanson et al., 2011). Organized breeding efforts have
used a common-garden approach with white mold screening nurseries in dry
bean production areas across the United States with additional sites in
Mexico, France, and Australia (Steadman et al., 2003, 2004, 2005, 2006;
Otto-Hanson \& Steadman, 2007, 2008; McCoy \& Steadman, 2009). These
white mold screening nurseries use no chemical or cultural treatments
against \emph{S. sclerotiorum} and employ standardized protocols for
screening new cultivars for resistance to white mold. It has previously
been shown that aggressiveness (the severity of disease symptoms on the
host) is significantly different across white mold screening nursery
sites in separate geographic regions (Otto-Hanson et al., 2011). The
genetic structure and mode of reproduction in these populations,
however, is currently unknown.

@@

In this study, we analyze and characterize the genetic and phenotypic
diversity of 366 \emph{S. sclerotiorum} isolates collected between 2003
and 2012 from dry bean cultivars among different geographic locations in
the United States, France, Mexico, and Australia. We wanted to know if
the \emph{S. sclerotiorum} populations from white mold screening
nurseries were representative of the fields within the same region. As
these nurseries were not treated with any chemical or cultural control
of white mold, we hypothesized that these nurseries would represent the
natural population of \emph{S. sclerotiorum}. Furthermore, we wanted to
investigate the potential effect of cultivar on genetic diversity of the
pathogen by assessing three dry bean cultivars with different levels of
resistance, Beryl (great northern bean, susceptible), Bunsi (navy bean,
low susceptibility), and G122 (cranberry bean, partial resistance)
(Otto-Hanson et al., 2011). We additionally wanted to determine
categorical or phenotypic variables that best predicted genetic
structure and if there was correlation between multilocus haplotype and
mycelial compatibility group. Knowing what variables predict genetic
structure can help direct breeding efforts. By investigating these aims,
we hope to effectively describe the population structure of \emph{S.
sclerotiorum} in the USA and make available our database of isolates for
use in future dry bean breeding efforts.

@@

Several of the isolates used for this study were collected as reported
in previous studies using the same methods (Otto-Hanson et al., 2011).
Broadly, isolates were collected from two sources: white mold screening
nurseries (wmn) or producer fields. White mold screening nurseries were
5m x 10m in size and maintained without application of fungicides to
observe natural incidence of white mold. The early nursery plots were
incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of
0:3:2 during the growing season (Steadman et al., 2003).

@@

Sclerotia of \emph{S. sclerotiorum} were collected over several years
from grower fields and/or wmn in 11 states of the United States of
America, Mexico, France, and Australia (Table \ref{tab:isolate-table}).
After collection, sclerotia were stored in Petri plates lined with
filter paper, then stored at \(20~^{\circ}\)F or -\(4~^{\circ}\)C.
Sclerotia were surface-sterilized with 50\% Clorox bleach (at least 6\%
NaOCL, The Clorox Company, Oakland, CA) solution for 3 min, and double
rinsed with ddH\(_2\)O for 3 min. The sterilized sclerotia were then
placed on water agar plates (16g of Bacto agar per liter of ddH\(_2\)O,
BD Diagnostic Systems, Sparks, MD), with four to five sclerotia of each
isolate separated on each plate and stored on the counter top at room
temperature for 5 to 6 days. An 8-mm plug from a 5- or 6-day-old culture
was transferred from the advancing margin of the mycelia onto a plate of
Difco potato dextrose agar (PDA at 39 g/liter of ddH\(_2\)O)
(Otto-Hanson et al., 2011). In combination with the 156 isolates
described previously, we collected 210 isolates for a total of 366
isolates (Otto-Hanson et al., 2011).

@@

Aggressiveness of each isolate was assessed using a straw test as
described in Otto-Hanson et al. (2011) that rated necrotic lesion size
(Petzoldt \& Dickson, 1996; Teran et al., 2006). Briefly, the straw test
uses 21-day-old G122 plants as the host in a greenhouse setting. Clear
drinking straws cut to 2.5 cm and sealed were used to place two mycelial
plugs of inoculum on the host plant after removing plant growth beyond
2.5 cm above the fourth node. Measurements of the necrotic lesion were
taken 8 days later using the Modified Petzoldt and Dickson scale of
1--9, where 1 is no disease and 9 is plant death (Petzoldt \& Dickson,
1996; Teran et al., 2006).

@@

Prior to DNA extraction, isolates were grown on PDA and plugs were
subsequently transferred to Potato Dextrose Broth (PDB) where they were
grown until there was significant mycelial growth, but before the
mycelial mat became solidified (4--5 days). Each mycelial mat was
collected in a filtered Büchner funnel, agar plugs removed, lyophilized
and pulverized manually in Whirl-pak® HDPE sampling bags (Sigma-Aldrich,
St.~Louis, MO). Lyophilized mycelia was then stored in microcentrifuge
tubes at -\(20~^{\circ}\)C until needed for DNA extraction. DNA from
25mg of pulverized mycelia was purified using a phenol-chloroform
extraction method followed by alcohol precipitation and evaporation,
suspending the DNA in 200\(\mu\)l TE (Sambrook et al., 1989). Suspended
DNA was stored at \(4~^{\circ}\)C until genotyping.

@@

After clone-correction on the hierarchy of Region/Source/Host/Year, we
were left with 318 isolates representing 165 MLHs (Table
\ref{tab:iatab}). The results show that most populations exhibited
relatively high amounts of genotypic diversity, with the exception of MI
and NE, which exhibited lower-than average \(E_5\) values. Mexico had
the lowest average value of gene diversity, \emph{h} and the lowest
\emph{eMLH}, suggesting low overall genetic diversity. Nearly all
populations showed evidence for linkage (Table \ref{tab:iatab}), which
serves as evidence for clonal reproduction or other forms of non-random
mating. The only exceptions are CA (\emph{P} = 0.043) and Australia
(\emph{P} = 0.052). Both of these populations showed only moderate
significance with \(\bar{r}_d\) values of 0.03 and 0.12, respectively.

\begin{longtable}[]{@{}rrllrl@{}}

@@

\begin{minipage}[b]{0.08\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright\strut

@@

\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright\strut

@@

\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut

@@

\begin{minipage}[t]{0.08\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright\strut

@@

\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright\strut

@@

\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut

@@

\begin{longtable}[]{@{}crrrrllrl@{}}

@@

\begin{minipage}[b]{0.12\columnwidth}\centering\strut

@@

@@

\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright\strut

@@

@@

\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright\strut

@@

\begin{minipage}[t]{0.12\columnwidth}\centering\strut

@@

@@

\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\raggedleft\strut

@@

\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut

@@

@@

\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/mcg-subgraph-with-context.pdf}
\caption{Associations between Mycelial Compatibility Groups and
Multilocus Haplotypes. \textbf{A)} Barplot of Mycelial Compatibility
Group (MCG) abundance in descending order. Singletons (46) were
truncated, leaving 41 MCGs. White bars represent sample counts and grey
bars represent counts of unique multilocus haplotypes (MLH). The
transparency of the bars represent the evenness of the distribution of
the MLHs within a given MCG. A dashed box surrounds the eight most
common MCGs representing \textgreater{}~51\% of the data. \textbf{B)}
Full graph-representation of the relationship between MCGs (open
circles) and MLHs (filled circles). Details in Fig. \ref{fullgraph}.
\textbf{C)} A subset of \textbf{B} representing the 8 most common MCGs
and their associated MLHs (dashed box in \textbf{A}). Filled nodes
(circles) represent MLHs and open nodes represent MCGs. Node area scaled
to the number of samples represented (range: 1--73). Numbers inside
nodes are the MLH/MCG label (if n \textgreater{} 1). Edges (arrows)
point from MLH to MCG where the weight (thickness) of the edge
represents the number of shared isolates (range: 1--19). Edges extending
from MLHs displayed to other MCGs are not shown.}\label{biggraph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Figure7Z.pdf}
\caption{Biplot showing five most influential explanatory variables
(arrows) overlayed on the first two eigenvectors of distance based
redundancy analysis of \emph{Sclerotinia sclerotiorum} isolates. The
length of the arrows are directly proportional to the strength of the
correlation between explanatory and molecular variables. Open circles
represent the 318 clone-corrected haplotypes in ordination
space.}\label{rda-biplot}
\end{figure}

\begin{figure}
\centering
\includegraphics{../../results/figures/publication/aggressiveness.pdf}
\caption{Strip Plot of aggressiveness by population arranged in
descending order of mean aggressiveness for all populations with N
\textgreater{} 5. White bars represent mean value. Circles represent
individual isolates where filled circles are isolates from white mold
screening nurseries (wmn) and open circles are isolates from producer
fields.}\label{aggressiveness-boxplot}
\end{figure}

The forward-backward selection process of the dbRDA models on
clone-corrected data revealed Year, Region, Host, and MCG to be the
optimal variables for the reduced model, accounting for 45\% of the
total variation. ANOVA showed that the reduced model was significant
with an adjusted R\textsuperscript{2} of 0.0675 (\emph{P} = 0.001).
Assessment of the marginal effects showed that all varaibles
significantly explained genetic variation (\(P \leq 0.007\)). We found
that there was multicollinearity when MCG was combined with any other
variable, so repeated the analysis, dropping MCG from the list of
potential predictors. From these results, Year, Region, Host, and
Aggressiveness were found to be optimal, accounting for 17.6\% of the
total variation. ANOVA revealed significant effects with an adjusted
R\textsuperscript{2} of 0.0325 (\emph{P} = 0.001). While the marginal
effect assessment revealed that Year, Region, and Host significantly
explained variation at \emph{P} = 0.001, and Aggressiveness
significantly explained variation at \emph{P} = 0.039. Much of the
variation appeared to be driven by isolates from Mexico and 2005 (Fig.
\ref{rda-biplot}). Variance partitioning of the independent variables
without MCG indicated aggressiveness to be the least influential factor
with 0.1\% contributing to explaining the variation of molecular data,
whereas the combination of variables accounted for 3.3\%.

@@

Agressiveness of the isolates ranged from 1.4 to 7.9 with a mean of 5.02
and median of 4.85. The group mean averages were 4.88, 5.13, and 5.19
for Region, MCG, and MLH, respectively. Our assessment of aggressiveness
in association with Region showed a significant effect (\emph{P}
\textless{} 1.00e\textsuperscript{-4}), with means that ranged from 5.8
(MN) to 4.0 (CA) (Fig. \ref{aggressiveness-boxplot}, Table
\ref{tab:region-aggressiveness}). MCGs also showed a significant effect
(\emph{P} \textless{} 1.00e\textsuperscript{-4}), with means that ranged
from 6.0 (`MCG 44') to 4.6 (`MCG 49'; Table
\ref{tab:MCG-aggressiveness}). We additionally found a significant
effect for MLHs (\emph{P} = 7.44e\textsuperscript{-4}), with means that
ranged from 6.0 (`MLH 78') to 4.3 (`MLH 140') (Table
\ref{tab:MLG-aggressiveness}).

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/mlg-11.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) genotyped over 11 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/DAPC.pdf}
\caption{Discriminant Analysis of Principal Components on regions
showing that Mexico is differentiated from other populations.
\textbf{A)} Scatter plot of first two components from DAPC. Points
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. \textbf{B)} Mean population assignment probability from the DAPC
for all populations with N \textgreater{} 10 (facets). Populations
represented along the horizontal axis and probability of assignment on
the vertical. Numbers next to source populations indicate population
size. All values sum to one.}\label{DAPC}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/dapc_region_year_micanewa.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
on Regions and Years showing non-differentiated temporal variation NE
and MI and temporal variation in WA and CA. Points (text labels)
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. A more detailed view is shown in Fig.
\ref{DAPC-RY-FULL}.}\label{DAPC-RY}
\end{figure}

@@

Despite the evidence that Mexico and CA contributed to much of the
population differentiation, Regions like WA still had a large amount of
internal variation. The two distinct clusters for the WA Region showed
that the 2008 population appeared differentiated and, under further
investigation, we found that all the haplotypes from this year were
shared between CA and France (Fig. \ref{community-graph}, \ref{DAPC-RY},
\ref{DAPC-RY-FULL}). All of the isolates from WA in 2003--2005, and 2008
came from the same wmn; within the wmn, those in 2003--2005 came a
Northeastern field location cropped with dry bean since 2002, and those
in 2008 from a Southeastern field that was previously cropped with
brassica, sundgrass, peas, beans, and potatoes (Miklas, Phil Pers.
comm.). Both of these fields were inoculated with sclerotia in 2002, the
Northeastern field with sclerotia provided by a commercial bean producer
and the Southeastern field with sclerotia from peas (although this was
thought to be unsuccessful). Despite this information, it is still
unclear what has contributed to the differentiation of the 2008
population from WA. While the evidence may suggest host as being a
factor, previous studies have shown no significant differentiation
across host species (Aldrich-Wolfe et al., 2015).

@@

One long-held assumption was that MCGs (as determined via barrage
reaction) represent vegetative compatibility groups (VCGs) (Kohn et al.,
1990; Schafer \& Kohn, 2006; Lehner et al., 2015), which are known to
have a genetic component (Saupe, 2000; Hall et al., 2010; Strom \&
Bushley, 2016). While our protocol for assessing MCGs utilized Diana
Sermons Medium (Cubeta et al., 2001) as compared to Patterson's Medium
or Potato Dextrose Agar (Schafer \& Kohn, 2006) for the MCG reactions,
the patterns we observe are not dissimilar from what have previously
been reported in the literature. It has been demonstrated in several
Ascomycetes---including \emph{Neurospora crassa} (Micali \& Smith,
2003), \emph{Sclerotinia homoecarpa} (Jo et al., 2008),
\emph{Verticillium dahliae} (Papaioannou \& Typas, 2014), and \emph{S.
sclerotiorum} (Ford et al., 1995)---that barrage reactions are
independent from stable anastomosis. Thus, the inconsistencies in this
study and other studies indicate that researchers studying \emph{S.
sclerotiorum} should not rely on MCG data derived from barrage reactions
as an indicator for genetic diversity.

@@

This study represents the largest genetic analysis of \emph{S.
sclerotiorum} from the USA to date, giving us a unique insight to
continent-wide population structure and relationships between phenotypic
and genotypic variables. Populations in wmn appear to show no
significant differentiation when compared to their production field
counterparts, suggesting that the wmn populations of \emph{S.
sclerotiorum} may be considered representative of the surrounding
regions. While we found no direct relationship between haplotype and
severity, it is evident that there is a gradient of severity by region,
further supporting the need for screening in multiple locations. Based
on our analysis of the relationships between MCG and MLH, we found no
clear evidence that the two are directly related, suggesting that MCG
does not necessarily represent vegetative compatibility groups and thus
should not be used as a proxy for identifying clones.
